Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-01 overall.tex
minor fixes in Section 4.

Figure~\ref{fig:backfill-utilization} (green bars) shows backfill utilization
during the experiment time window. Efficiency
(Figure~\ref{fig:backfill-utilization}, red labels) is defined as the fraction
of Titan’s cores available via backfill that was utilized by the PanDA Brokers.
The brokers reached 18\% average efficiency, with a minimum 8.9\% efficiency on
April 2016 and a maximum 33.5\% efficiency on February 2017. The number of total
backfill cores available was 38.1M in April 2016, and 33.1M in February 2017.
This shows that the measured difference in efficiency did not depend on a
comparable difference in total backfill availability.

@@

\begin{figure}[htp]
    \includegraphics[clip,width=\columnwidth]{figures/titan_backfill_avail.png}
    %figures/avail_time_vs_nodes_Oct_28_Nov_3_2015.pdf}
    \caption{Backfill availability measures as walltime in minutes vs number of
    work nodes during the experiment window time. Availability was measured
    62175 times: mean number of work nodes available 680 (yellow line); mean
    walltime available 122 minutes (red line).}
\label{fig:backfill-distrib}
\end{figure}

>>>>

Figure~\ref{fig:backfill-utilization} (green bars) shows backfill utilization
during the experiment time window.  Efficiency 
(Figure~\ref{fig:backfill-utilization}, red labels) is defined as the fraction of core-hours utilized by
the PanDA Brokers (for ATLAS jobs) to the total of Titan’s backfill
availability. The brokers reached 18\% average efficiency, with a minimum
8.9\% efficiency on April 2016 and a maximum 33.5\% efficiency on February
2017. The total backfill available was 38.1M core-hours in April 2016,
and 33.1M core-hours in February 2017. This shows that the measured difference in
efficiency did not depend on a comparable difference in total backfill
availability.

@@

\begin{figure}[htp]
    \includegraphics[clip,width=\columnwidth]{figures/titan_backfill_avail.png}
    %figures/avail_time_vs_nodes_Oct_28_Nov_3_2015.pdf}
    \caption{Backfill availability measures as walltime in minutes vs number of
    work nodes during the experiment window time. Availability was measured
    62175 times: mean number of work nodes available 680 (orange line); mean
    walltime available 122 minutes (red line).}
\label{fig:backfill-distrib}
\end{figure}
